---
title: "Figure 1G"
author: "Kate McDaniel"
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---
## Setting up the data for analysis

```{r, include=FALSE}
#setwd()

library(readxl)
library(plotly)
library(tidyverse)
library(dplyr)
library(rstatix)
library(car)
library(DescTools)

```

```{r, echo = FALSE}
file.list <- c(dir(pattern = ".xlsx"))
path <- paste0(getwd(), "/", file.list)
sheet.name <- excel_sheets(path = path)

#initializing lists I'll need later so they don't get caught in the for loops that I write for them
list.dfs <- list()


#pulling all the files in 
for (a in file.list){
  for (i in sheet.name) {
    #assign(paste0(i), read_excel(file.name, sheet = i, skip = 1, col_names = TRUE, trim_ws = TRUE))
    list.dfs <- c(list.dfs, list(read_excel(a, sheet = i, skip = 0, col_names = TRUE, trim_ws = TRUE)))
  }
}

names(list.dfs) <- sheet.name
```


#selecting just the FL data to run stats on.

I am assumption testing and then running either an ANOVA or Kruskall Wallis with correction for multiple comparisons. I'll do a Dunnett Test for multiple comparisons because I want to compare everything to DMSO.

```{r, stats preparation for FL, echo = FALSE}
#going to test these stats because I think the ANOVAs are probably more 
index <- "FL"
include <- lapply(list.dfs, function(x) x[x$Size == index,])
include <- bind_rows(include, .id = "Experiment")

#assumptions
model <- lm(include$`Over DMSO` ~ include$Condition)
results <- shapiro.test(rstandard(model)) 
results

significant <- results$p.value >= 0.05
print("Meets Normality?")
print(significant)

print("DMSO QQ Plot")
test <- subset(include, Condition == "DMSO")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

print("DAPT QQ Plot")
test <- subset(include, Condition == "DAPT")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

print("PMA QQ Plot")
test <- subset(include, Condition == "PMA")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

print("DAPT+PMA QQ Plot")
test <- subset(include, Condition == "DAPT + PMA")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

#testing for heterogeneity of variance
include$Condition<- factor(include$Condition)
results <- leveneTest(include$`Over DMSO` ~ include$Condition, center = mean)
results 

significant <- results$`Pr(>F)` >= 0.05
print("Meets Homogeneity of Variance?")
print(significant[1])

#running kruskall wallis becuase homogeneity of variance is not significant and normality probably isn't for multiple of these guys

kruskal.test(`Over DMSO` ~ Condition, data = include)
DunnettTest(`Over DMSO` ~ Condition, data = include, control = "DMSO")


```


#selecting just the ICD data to run stats on.

I am assumption testing and then running either an ANOVA or Kruskall Wallis with correction for multiple comparisons. I'll do a Dunnett Test for multiple comparisons because I want to compare everything to DMSO.
```{r, stats preparation for CTF, echo = FALSE}
index <- "CTF"
include <- lapply(list.dfs, function(x) x[x$Size == index,])
include <- bind_rows(include, .id = "Experiment")

#assumptions
model <- lm(include$`Over DMSO` ~ include$Condition)
results <- shapiro.test(rstandard(model)) 
results

significant <- results$p.value >= 0.05
print("Meets Normality?")
print(significant)

print("DMSO QQ Plot")
test <- subset(include, Condition == "DMSO")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

print("DAPT QQ Plot")
test <- subset(include, Condition == "DAPT")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

print("PMA QQ Plot")
test <- subset(include, Condition == "PMA")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

print("DAPT+PMA QQ Plot")
test <- subset(include, Condition == "DAPT + PMA")
qqnorm(test$`Over DMSO`, pch = 1)
qqline(test$`Over DMSO`)

#testing for heterogeneity of variance
include$Condition<- factor(include$Condition)
results <- leveneTest(include$`Over DMSO` ~ include$Condition, center = mean)
results 

significant <- results$`Pr(>F)` >= 0.05
print("Meets Homogeneity of Variance?")
print(significant[1])

#running kruskal wallis 
kruskal.test(`Over DMSO` ~ Condition, data = include)
DunnettTest(`Over DMSO` ~ Condition, data = include, control = "DMSO")


```

